% resume122425.tex
% Qompass AI Resume Template
% Copyright (C) 2025 Qompass AI, All rights reserved
% ----------------------------------------

\documentclass[9pt,a4paper]{article}
\usepackage{geometry}
\geometry{left=1.9cm,right=1.9cm,top=1.5cm,bottom=1.5cm}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{titlesec}
\newenvironment{expitemize}{%
  \begin{itemize}[leftmargin=*, topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt]
}{%
  \end{itemize}
}
\newfontfamily\emoji{Noto Color Emoji}
\newcommand{\emojiDoc}{{\emoji 📑}}
\newcommand{\emojiTalk}{{\emoji 🎤}}
\newcommand{\emojiPoster}{{\emoji 🖼}}
\newcommand{\emojiOther}{{\emoji 📝}}
\newcommand{\sectionline}{%
  \nointerlineskip
  \vspace{0.25em}%
  \hspace*{-\hoffset}\hspace*{-\oddsidemargin}%
  \rule{\dimexpr\textwidth+\hoffset+\oddsidemargin\relax}{0.4pt}%
  \vspace{0.4em}%
}

\newcommand{\centersection}[1]{%
  \vspace{0.6em}%
  \begin{center}
    \large\bfseries #1%
  \end{center}
  \sectionline
}
\setlength{\parindent}{0pt}
\setstretch{1.08}
\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing{\section}{0pt}{0.5em}{0.25em}

\begin{document}
\begin{center}
    {\Huge Matthew (Matt) Anthony Porter}\\[4pt]
    Email: \href{mailto:map@qompass.ai}{map@qompass.ai}\\[2pt]
    \quad|\quad
    Phone: 509--919--5237
    \quad|\quad
    GitHub: \href{https://github.com/qompassai}{qompassai} \quad•\quad
    \href{https://github.com/phaedrusflow}{phaedrusflow} \quad•\quad
    HuggingFace: \href{https://huggingface.co/qompass}{qompass}
\end{center}

\vspace{0.7em}

\section*{Education}

\begin{itemize}[leftmargin=*]
  \item \textbf{Washington State University Elson S. Floyd College of Medicine, Spokane WA} \hfill 08/20--04/25\\
  (Leave of Absence 03/23--12/24; withdrew 04/25)

  \item \textbf{Pierce Community College, Ft. Steilacoom, WA} -- Emergency Medical Services Certificate \hfill 01/19--03/19

  \item \textbf{United States Military Academy, West Point NY} -- Class of 2011, B.S.\ in Life Sciences with Honors, Nuclear Engineering Track \hfill 07/07--05/11
\end{itemize}

% \section*{Awards}
\centersection{Awards}

\textbf{Funding:}\\
2024 Evergreen Internship Development Incentive (\$2{,}000);
2024 Zimmer Biomet Startup Pre-Seed Grant (\$30{,}000);
2023 Perry Initiative Orthopaedics in Action Grant (\$2{,}000);
2022 Health Sciences Chancellor’s Excellence Award for Leadership (\$1{,}000);
2022 WSU Shikany Service Award (\$1{,}000);
2022 WSU Carson Veteran Scholarship (\$1{,}000);
3$\times$ Founding Dean's Research Grant Recipient (\$5{,}000);
WSU Research Travel Grant (\$875).

\textbf{Certifications:}\\[-0.9\baselineskip]
\begin{expitemize}
  \setlength{\topsep}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\partopsep}{0pt}
  \setlength{\itemsep}{0pt}
  \item Anaconda: Certified Python Instructor.
  \item Microsoft: Microsoft Certified Educator; Azure Data Science, Data Engineer, Security Engineer.
  \item Google: Project Management, Cybersecurity, Business Intelligence, Digital Marketing.
  \item Medical: Johns Hopkins Health IT; EMT-Basic (EMS ID 3725--5746--8319).
\end{expitemize}

\vspace{0.2em}
\textbf{Honors \& Military Awards:}\\
Bronze Star; Army Commendation Medal (2); Army Achievement Medal;
Afghanistan Campaign Medal with Campaign Star;
Global War on Terrorism Service Medal;
Korea Defense Service Medal;
National Defense Service Medal;
German Armed Forces Proficiency Badge;
Army Service Ribbon;
Overseas Service Ribbon;
NATO Medal.

\vspace{0.4em}
% \section*{Skills}
\centersection{Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Code:} Python, Rust, Lua, JavaScript, C++ (Unreal), Go, Zig, CUDA, Mojo.
  \item \textbf{NetOps:} IPv6/IPv4, DNS, SSL/TLS, SSH, GPG/PGP, Tor. Docker/Podman, Kubernetes
  \item \textbf{DevOps:} Bash, Kernel, Terraform, Ansible, Postgres, MySQL/MariaDB, SQLite, Redis/Valkey, Vulkan, Git.
  \item \textbf{OS:} Windows 10/11; macOS; Linux (Debian, Ubuntu, Arch, Nix, Fedora).
  \item \textbf{Med:} CPR, BLS, HIPAA compliance, publication.
  \item \textbf{Mil:} Project management, leadership, civil/military relations.
  \item \textbf{Edu:} Teaching, tutoring, curriculum development.
\end{itemize}

% \section*{Experience}
\centersection{Experience}

\textbf{Community Connections Incorporated, Post Falls, ID -- Direct Support Professional} \hfill 07/25--Current\\
\begin{itemize}[leftmargin=*]
  \item Collaborate with families and interdisciplinary teams to implement individualized support plans and promote independence and social-emotional growth for disabled participants.
\end{itemize}

\textbf{Qompass AI, Spokane, WA -- Technologist Consulting} \hfill 03/23--Present\\[-0.25\baselineskip]
\begin{expitemize}
  \item Consult on healthcare AI integration and data workflows; secured a \$30{,}000 Zimmer Biomet Foundation grant for a generative AI medical education pilot.
  \item Designed and led the PathFinder Intern program, winning a \$2{,}000 Greater Spokane Incorporated grant and training 12 interns in Python, data analysis, and AI tools.
\end{expitemize}

\textbf{NASS|MSOS|Pixorize|MedAll|Elsevier, Spokane, WA -- Education Ambassador} \hfill 06/22--03/23\\[-0.25\baselineskip]
\begin{expitemize}
  \item Coordinated mentorships for 22 underrepresented medical students across 14 medical schools with 13 longitudinal mentors, improving access to specialty advising and research.
\end{expitemize}

\textbf{WSU Elson S. Floyd College of Medicine, Spokane, WA -- Student Educational Leader} \hfill 06/21--03/23\\[-0.25\baselineskip]
\begin{expitemize}
  \item Founded an AI-enabled youth outreach program, raising \$10{,}000 and engaging over 8{,}000 youth in STEM
    and para-education careers.
  \item Built a multi-site community research mentorship network for 20 students supervised by five MD/PhD researchers.
  \item Developed the college’s first AI-driven educational knowledge platform, adopted enterprise-wide with 8{,}000+ uses.
  \item Co-founded three student organizations and led 10+ events, establishing partnerships with two residency programs and three hospital systems.
\end{expitemize}

\textbf{Spanaway Community Healthcare Clinic, Spanaway, WA -- Acute Care Medical Scribe} \hfill 08/19--03/20\\[-0.25\baselineskip]
\begin{expitemize}
  \item Documented high-volume free acute care visits in real time and supported labs and referrals, including Project Access care coordination.
\end{expitemize}

\textbf{U.S. Army Active Duty, Various (AZ, KR, CO, AF, WA) -- Intelligence Officer (Top Secret Clearance)} \hfill 05/11--06/19\\[-0.25\baselineskip]
\begin{expitemize}
  \item Led a 74-soldier support company and \$40{,}000{,}000 in equipment as Detachment Commander / Director.
  \item Directed 1{,}000+ intelligence collection operations, coordinating with international partners, Palantir, and national intelligence agencies during elections and provincial transitions.
  \item Planned and oversaw international intelligence operations and training programs for eight deployed tactical intelligence teams.
  \item Served as Brigade Intelligence Officer and communications / public affairs lead, supporting the Northwest Joint Regional Correctional Facility.
\end{expitemize}

\textbf{Tacoma Neighborhood Free Clinic, Tacoma, WA -- Volunteer Emergency Technician} \hfill 07/19--03/20\\
\begin{itemize}[leftmargin=*]
  \item Conducted patient intake, assisted with labs, and coordinated referrals for uninsured patients, including Project Access services.
\end{itemize}

\textbf{Multicare Allenmore Emergency Department, Tacoma, WA -- Volunteer Trainer / ER Volunteer} \hfill 10/18--03/20\\
\begin{itemize}[leftmargin=*]
  \item Selected as ER Volunteer Trainer for exceptional clinical support; onboarded and trained 15 new volunteers.
\end{itemize}

\textbf{Village Seven Presbyterian Church, Colorado Springs, CO -- Church Youth Instructor} \hfill 07/13--12/13\\
\begin{itemize}[leftmargin=*]
  \item Led weekly classes and mentoring for 15 elementary-age youth, supporting social-emotional growth and academic habits.
\end{itemize}

\textbf{United States Military Academy, West Point, NY -- Cadet Leader} \hfill 08/07--05/11\\
\begin{itemize}[leftmargin=*]
  \item Regimental Academic Officer, American Chemical Society Youth Mentor, United States Military Academy
    Preparatory School (USMAPS) Basic Training Deputy Director, Special Olympics Partner, Company Intramural Athlete: Biathlon, Swim, Ultimate Frisbee  
\end{itemize}

\section*{Publications}

\textit{Legend:}
\emojiDoc\ Manuscript \quad
\emojiTalk\ Podium Presentation \quad
\emojiPoster\ Poster \quad
\emojiOther\ Other than Published\\
38 publication works, 8 citations, h-index 2; 2 peer reviews.


\vspace{0.4em}
\textbf{Manuscripts (\emojiDoc)}
\begin{enumerate}[leftmargin=*]
  \item \textbf{Clinical Orthopaedics and Related Research (CORR), 2024}\\
  PORTER M.\ A., BS. ``Value-based Healthcare: Can Generative Artificial Intelligence and Large Language Models be a Catalyst for Value-based Healthcare?''\\
  DOI: 10.1097/CORR.000000000000300; PMID 38456784.

  \item \textbf{Arthroplasty Today, 2023}\\
  PORTER M.\ A., BS, Johnston M.\ G., MA, Kogan K., PhD, Gray C., BS, Eppich K., BS, Scott D.\ F., MD. ``The Joint Awareness Score: A Shortened, Simplified Alternative to the Forgotten Joint Score.''\\
  DOI: 10.1016/j.artd.2023.101239; PMCID: PMC10641080.

  \item \textbf{Journal of Bone \& Joint Surgery Case Connector, 2022}\\
  PORTER M.\ A., BS, Schmitz M., MD. ``Posterior Reversible Encephalopathy Syndrome with Post-Operative Hematoma Following C4--C6 Spinal Fusion: A Case Report.''\\
  DOI: 10.2106/JBJS.CC.21.00700; PMID 35763013.

  \item \textbf{International Journal of Surgery Case Reports, 2021}\\
  PORTER M.\ A., BS, Schmitz M., MD. ``ACDF and posterior spinal fusion revision for posterior nonunion with deformity, myelopathy, and osteoporosis in an 87-year-old: A Case Report and Literature Review.''\\
  DOI: 10.1016/j.ijscr.2021.106650; PMCID: PMC8715042.

  \item \textbf{Cureus, 2022}\\
  Frolov D., BS, PORTER M.\ A., BS, Schmitz M., MD. ``Posterior Cervical Fusion of Occiput--T3 for Unstable Complex Odontoid Fracture in an 80-year-old Male with C2--Sacrum Synostosis from Ankylosing Spondylitis: A Case Report.''\\
  DOI: 10.7759/cureus.26897; PMCID: PMC9376032.
\end{enumerate}

\vspace{0.4em}
\textbf{Podiums (\emojiTalk)}
\begin{enumerate}[leftmargin=*,resume]
  \item 2025 American Academy of Orthopaedic Surgeons Annual Meeting\\
  PORTER M.\ A., BS, Rowshan A., BA, Hill M.\ J., DO, Laporte D.\ M., MD, Aiyer A.\ A., MD. ``The Responsible Open Science Engine: Powering Minimally Invasive AI for Mentorship.''\\
  DOI: 10.5281/zenodo.14842431.

  \item 2023 Western Orthopaedic Association Stryker Innovation Contest\\
  PORTER M.\ A., BS. ``All For One \& One For All: An Amplifying Intelligence Framework for Orthopaedics.''

  \item 2022 Western Medical Research Conference\\
  PORTER M.\ A., BS, Telis A., MD, Johnston M., MA. ``Complex Lower Left Leg Deformity Correction with PRECICE System: A Case Report and Review of the Literature.''\\
  DOI: 10.1136/jim-2022-WRMC.

  \item 2022 American College of Surgeons Washington-Oregon Regional Conference\\
  PORTER M.\ A., BS, Lewis S., BS, Mechtly C., PharmD, Birch J., BS, Sampson S., MD, Schaetzel S., MD, Oh K., MD, Glaser J., MD. ``Giving Patients What They Bleed: Initial Result From a New Regional Whole Blood Program.''

  \item 2022 Eastern Medical Research Conference\\
  PORTER M.\ A., BS, Johnston M., MA, Rusev M., MA, Schmitz M., MD. ``Radial Styloid Approach for Unstable Distal Radius Fracture Open Reduction and Internal Fixation.''\\
  DOI: 10.1136/jim-2022-ERM.

  \item 2022 Health Occupation Students of America Washington State Leadership Conference\\
  PORTER M.\ A., BS, Nielsen P., BS, Jones B., Johnston M., MA, Schmitz M., MD. ``Joined at the Hip: Leadership \& Orthopaedics.''\\
  DOI: 10.13140/RG.2.2.13648.58885.

  \item 2023 Health Occupation Students of America Washington State Leadership Conference\\
  PORTER M.\ A., BS, Schmitz M., MD. ``The Mission of Mentorship: The Marrow of Orthopaedics.''\\
  DOI: 10.13140/RG.2.2.16748.44165/1.
\end{enumerate}

\vspace{0.4em}
\textbf{Posters (\emojiPoster)}
\begin{enumerate}[leftmargin=*,resume]
  \item 2025 American Academy of Orthopaedic Surgeons Annual Meeting\\
  PORTER M.\ A., BS, Rowshan A.\ P., BS, Hill M.\ J., DO, Laporte D.\ M., MD, Aiyer A.\ A., MD. ``The Responsible Open Science Engine: Powering Minimally Invasive AI for Mentorship.''

  \item 2024 American Medical Association Research Challenge\\
  PORTER M.\ A., BS, Hill M.\ J., DO, Laporte D.\ M., MD, Aiyer A.\ A., MD. ``Kyber Odyssey: Charting a Course for Secure Innovation in a Post-CrowdStrike World.''\\
  DOI: 10.48448/kwd5-1j32.

  \item 2022 Eastern Medical Research Conference\\
  PORTER M.\ A., BS, Schmitz M.\ A., MD. ``Clinical Evidence Towards Hypertensive Pathogenesis of Posterior Reversible Encephalopathy Syndrome in the Setting of Spinal Fusion.''\\
  DOI: 10.1136/jim-2022-ERM.

  \item 2022 Midwest Clinical and Translational Research Meeting\\
  PORTER M.\ A., BS, Schmitz M.\ A., MD. ``Multi-Stage Combined Anterior-Posterior Decompression and Fusion as Corrective Intervention in Octogenarian Population with Prior Spinal Fusion Attempt and Pseudarthrosis.''\\
  DOI: 10.1136/jim-2022-WRMC.

  \item 2022 Northwest Inland Imaging Research Symposium\\
  PORTER M.\ A., BS, Lewis S., BS, Mechtly C., PharmD, Birch J., BS, Sampson S., MD, Schaetzel S., MD, Oh K., MD, Glaser J., MD. ``Giving Patients What They Bleed: Initial Result From a New Regional Whole Blood Program.''

  \item 2022 American Academy of Physical Medicine and Rehabilitation Annual Assembly\\
  Frolov D., BS, PORTER M.\ A., BS, Schmitz M.\ A., MD. ``Posterior cervical fusion of occiput--T3 for unstable complex odontoid fracture in an 80-year-old male with C2--sacrum synostosis from ankylosing spondylitis: A Case Report and Review of the Literature.''\\
  DOI: 10.1002/pmrj.12913.
\end{enumerate}

\vspace{0.4em}
\textbf{Other (\emojiOther)}
\begin{enumerate}[leftmargin=*,resume]
  \item \textbf{JBJS Open Access}\\
  Rowshan A.\ P., BS, PORTER M.\ A., BS, Laporte D.\ M., MD, Aiyer A.\ A., MD. ``Comparing AI-Based Human Medical Scribes: Orthopaedic Surgeons’ Preferences and Perceptions.''\\
  Publication status: accepted June 22, 2025.

  \item \textbf{NEJM AI}\\
  PORTER M.\ A., BS, Laporte D.\ M., MD, Aiyer A.\ A., MD. ``Transforming Knowledge Ontology with the Model Context Protocol.''\\
  Publication status: manuscript in drafting.
\end{enumerate}

\section*{Personal Interests}

Motorcycling, programming, and spending time with wife Katy and dogs Dempsey and Zen.

\end{document}

